The \dealii{} Library, Version 9.3

### 2021-06-17 9.3/paper.tex
Fix some affiliations
Fix typo

\author[7]{Sebastian~Proell}

@@

\author[4]{Jiaqi~Zhang}

@@

While \texttt{FEPointEvaluation} assumes that evaluation points are already sorted according to 
the owning cells and thus can focus on cell-local operations, the new class
\texttt{RemotePointEvaluation} is responsible for determine the owning cells in a distributed
context and for providing efficient communication patterns for the data exchange. In \texttt{deal.II},
the class has been successfully applied together with \texttt{FEPointEvaluation} to evaluate a distributed
solution vector at arbitrary points (see also the
\texttt{VectorTools::point\_values()} function).

>>>>

\author[8]{Sebastian~Proell}

@@

\author[5]{Jiaqi~Zhang}

@@

While \texttt{FEPointEvaluation} assumes that evaluation points are already sorted according to 
the owning cells and thus can focus on cell-local operations, the new class
\texttt{RemotePointEvaluation} is responsible for determining the owning cells in a distributed
context and for providing efficient communication patterns for the data exchange. In \texttt{deal.II},
the class has been successfully applied together with \texttt{FEPointEvaluation} to evaluate a distributed
solution vector at arbitrary points (see also the
\texttt{VectorTools::point\_values()} function).
